---
title: "EDA"
author: '16009480'
date: "13/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Firstly, we'll look at the cqcData. Each row is a healthcare facility in England and each has information about the location (i.e. location details), information about the facility (i.e. owner) and most importantly about the rating itself. 

The lat an long were added in previous R code. It is known there are some missing values. 

The regions will be the same as the region information in money csv



```{r CQC Ratings}
cqcData = read.csv("/home/ojba/Documents/University_Work/DALT7016/rshiny_NHS_data/Data_Files/cqc_long_lat.csv")

names(cqcData)
unique(cqcData$Domain)
unique(cqcData$Location.Region)


```

## Understanding CQC data

Want to see: 
- Total ratings (including by regions)
- Facilities by region
- Identify Missing Data
- Healthcare Facilities

#Info (from below)
- 74186 total ratings. 
- First graph for total ratings by region 
- Wales was dropped as it is psuesdo 
- Graphs of ratings, percentage shows that London and Yorkshire have the most Good ratings. 
North east has the most outstanding
-Missing Data - for the most important columns looks fine, 212 missing lat and long values, this was an issues in lat long lib. 

```{r pressure, echo=FALSE}
library(dplyr)
library(ggplot2)

cqcData = cqcData[which(cqcData$Location.Region!="(pseudo) Wales"), ]
dim(cqcData)
total_ratings = cqcData %>% count(Latest.Rating)
ggplot(data = total_ratings, aes(x = Latest.Rating, y = n) ) + geom_bar(stat = "identity", color = "blue", fill = "blue")

by_region = cqcData %>% count(Location.Region, Latest.Rating, sort = T) %>% arrange(Latest.Rating)
ggplot(data = by_region, aes(fill = Latest.Rating, x = Location.Region, y = n), width = 1000) + geom_bar( stat = "identity", width = 0.5) + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

by_region = cqcData %>% count(Location.Region, Latest.Rating, sort = T) %>% arrange(Latest.Rating)
ggplot(data = by_region, aes(fill = Latest.Rating, x = Location.Region, y = n)) + geom_col(position = "fill") + theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))


sum(is.na(cqcData$Location.Region))
sum(is.na(cqcData$Latest.Rating))
sum(is.na(cqcData$Location.Post.Code))
sum(is.na(cqcData$lat))
sum(is.na(cqcData$long))
sum(is.na(cqcData$Location.Name))
sum(is.na(cqcData$Provider.Name))
sum(is.na(cqcData$URL))

missingLatLong = cqcData[which(is.na(cqcData$lat) & is.na(cqcData$long)), ]
missingLatLong$Location.ID

```
## We also want to check to see the distribution of institutions


```{r fig.height=7, fig.width=15}
levels(cqcData$Location.Primary.Inspection.Category)

by_category = cqcData %>% count(Location.Primary.Inspection.Category, sort = T)

by_category_no_GP_Social_Care = by_category[-which(by_category$Location.Primary.Inspection.Category == "GP Practices" | by_category$Location.Primary.Inspection.Category == "Community based adult social care services"), ]

ggplot(by_category, aes(x="", y = n, fill = Location.Primary.Inspection.Category)) + geom_bar(width = 1, stat = "identity") + coord_polar("y", start = 0) + theme(legend.position = "bottom", legend.text = element_text(size = 7))

ggplot(by_category, aes(x=reorder(Location.Primary.Inspection.Category, -n), y =n )) + geom_bar(width = 0.8, stat = "identity")+ theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

ggplot(by_category_no_GP_Social_Care, aes(x=reorder(Location.Primary.Inspection.Category, -n), y =n )) + geom_bar(width = 0.8, stat = "identity")+ theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

```

## We can then check out the funding data. 

```{r}
fundingData = read.csv("final_pop_fund_data.csv")
names(fundingData)


```
```{r}
fundingYearData = fundingData[c("X2015.16", "X2016.17", "X2017.18", "X2018.19", "X2019.20")]


fundingYearData = data.frame(t(fundingYearData[-1]))
colnames(fundingYearData) = fundingData$NUTS.Region
fundingYearData$Date = rownames(fundingYearData)
rownames(fundingYearData) = 1:4

ggplot(data = fundingYearData, aes(x = Date, y = NORTHWEST, group = 1)) + geom_line() + labs(x = date, y = "NORTH WEST")


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
